TITLE

### 2021-02-25 outputs/Paper.Rmd
update

library(ggplot2)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

@@

```{r restaurant_type, echo=FALSE}

@@

# Treated group
rt1<-
  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Treated Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

@@

# Control group
rt2<-
  ggplot(control_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Control Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

@@

### correlation matrix
```{r correlation, echo=FALSE, fig.width=10, fig.height=4}

>>>>

library(ggplot2)
library(ggthemes)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 30, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_calc()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

@@

```{r restaurant_type, echo=FALSE,fig.width=12, fig.height=4}

@@

# Treated group
rt1<-
  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Treated Group: Restaurant Types") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

@@

# Control group
rt2<-
  ggplot(control_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Control Group: Restaurant Types") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

@@

### correlation matrix
```{r correlation, echo=FALSE, fig.width=20, fig.height=20}
#install.packages("fastDummies")
library(fastDummies)
Dummy_data<-simulated_data[-c(1,2,10)]

Dummy_data<- fastDummies::dummy_cols(Dummy_data)

# correlation matrix for Big restaurants
Dummy_data<-Dummy_data[-c(1:3,5:10,12,43)]

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1)

# Compute a matrix of correlation p-values
#install.packages("ggcorrplot")
library(ggcorrplot)
p.mat <- cor_pmat(Dummy_data)

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot1 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
corr.plot1

# correlation matrix for Small restaurants
Dummy_data<-simulated_data[-c(1,2,10)]
Dummy_data<- fastDummies::dummy_cols(Dummy_data)
Dummy_data<-Dummy_data[-c(1:3,5:10,12,42)]

# Compute a correlation matrix
corr <- round(cor(Dummy_data), 1)

# Compute a matrix of correlation p-values
library(ggcorrplot)
p.mat <- cor_pmat(Dummy_data)

# Visualize the lower triangle of the correlation matrix
# Barring the no significant coefficient
corr.plot2 <- ggcorrplot(
  corr, hc.order = TRUE, type = "lower",
  p.mat=p.mat
  )
corr.plot2

ggarrange(
  corr.plot1, corr.plot2, 
  labels = c('Big restaurant', 'Small restaurant'),
  ncol = 2, nrow = 1,
  align = "hv"
  )
